### 2019-04-05 5_evaluation.tex
Code for memory graph (currently commented out).
Text for memory-bound kernels.

\subsection{Peak Performance and Efficiency}
\label{subsec:peak-performance-and-efficiency}

@@

@@

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.3\times$ to $59\times$ (median $3.0\times$). From 1 to 3
dependencies, the ratio varies from $1.2\times$ to $15\times$ (median
$2.1\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 us with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible.

For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

>>>>

\subsection{Compute-Bound Performance}
\label{subsec:peak-performance-and-efficiency}

@@

\subsection{Memory-Bound Performance}

\input{e7_bytes}

Figure~\ref{fig:bytes} shows the performance of Task Bench
implementations with a memory-bound kernel. We measure peak memory
bandwidth of 108 GB/s, which compares favorably with the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} which report betweeen
79 and 90 GB/s.

Not all cores are required to saturate memory bandwidth. As a result,
systems that reserve one or more cores are able to hit 100\% of peak
performance, unlike with compute-bound kernels. Otherwise the
performance curves are similar. We are currently investigating the
performance of Charm++.

The remaining experiments use compute-bound kernels.

@@

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.3\times$ to $59\times$ (median $3.0\times$). From 1 to 3
dependencies, the ratio varies from $1.2\times$ to $15\times$ (median
$2.1\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 us with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible. For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.
